%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://afrid.in/}{\Large Afrid Hussain}} & Email :  \href{mailto:afridhussain.d@gmail.com}{afridhussain.d@gmail.com}\\
  \href{https://www.linkedin.com/in/afridhussain/}{LinkedIn |} 
  \href{https://github.com/afrid18/}{Github}& Mobile :  +91-703-237-6276 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sri Venkateswara college of Engineering and Technology}{Chittoor}
      {B.Tech in Computer Science and Engineering;  GPA: 2.96 | 7.4/10 }{August 2019 - April 2023}
    \resumeSubheading
      {Narayana Jr. College}{Guntakal, India}
      {Board of Intermediate Andhra Pradesh); 9.01 CGPA
}{June 2017 - April 2019}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
     \textbf{Languages}{: Python, Javascript, Typescript, Go, Java, C++, SQL, NoSQL, HTML, CSS/SASS }
     }
 \resumeSubItem{}{
	\textbf{Technologies and Frameworks}{: Linux System Administration, FastAPI(python), Blockchain  }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Citicorp}{Chennai}
      {Full Stack Developer - Full time}{July 2019 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Part of the Citi Retail Services (CRS) Acquisitions team that serves over 35 partners in the NAM region. }
        \resumeItem{}
        {Followed the Agile model and worked extensively in Angular, Java Springboot Microservices and PCF cloud technologies for deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {Hack For Social Good (SPI Cinemas)}{Chennai}
      {UI/UX Analyst - Intern}{May 2018 - Jul 2018}
      \resumeItemListStart
      \resumeItem{}
          {Part of the team of knowledge workers that brainstormed UI/UX Design ideas for aspiring startups.}
        \resumeItem{}
          {Restructured the User Interface for their website using Bootstrap framework, CSS, HTML and Vanilla Javascript.}
      \resumeItemListEnd

    \resumeSubheading
      {Kognify}{Chennai}
      {Full Stack Developer - Intern}{Dec 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{}
          {Created an automation tool using Angular and Material Design concepts to generate responsive static websites from a JSON file.}
         \resumeItem{}
          {Worked on HTTP communications(REST) and AdonisJs at the back-end.}
      \resumeItemListEnd
     \resumeSubheading
      {Check Health}{Chennai}
      {Software Developer - Intern}{Jun 2017 - Jul 2017}
      \resumeItemListStart
        \resumeItem{}
          {Used Ionic framework to create the profile page section for their hybrid app.
         }
         \resumeItem{}
          {Worked on Firebase for the back-end.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Mapping Virtual 3D Objects Onto the Face}
      {An attempt at reducing the time complexity of facial augmented reality algorithms by reducing the number of contour points used to detect orientation of the face.}
    \resumeSubItem{SSN Code Busters}
      {An online programming judge and platform developed using SQLite-Django-Bootstrap.}
  \resumeSubHeadingListEnd

%-------PUBLICATIONS------------------  
\section{Publications}
 \resumeSubHeadingListStart
  \resumeSubItem{}{Dr.T Shree Sharmila, Hemang Shah and Aadhithya Dinesh,
  \textbf{Analysis of facial landmark features to determine the best subset for finding facial orientation}, 2nd IEEE International Conference on Computational Intelligence in Data Science, (ICCIDS), February 21 – 23, 2019.}
 \resumeSubHeadingListEnd

%---------------------------------------
\section{Accomplishments}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
    \textbf{Finalist}{ - SSN Best Speaker Contest} {,2017 and 2018.}
    }
    \resumeSubItem{}{
    \textbf{Sanction Letter}{ - College Funded Project}{, SSN Code Busters, 2016. }
    }
    \resumeSubItem{}{
    \textbf{Placed 8th}{ - Shaastra Programming Contest Finals IIT Madras, 2016.}
    }
    \resumeSubItem{}{
    \textbf{Winner}{ - Inter College Math Quiz(SSN 2klog16), 2016.}
    }
    
 \resumeSubHeadingListEnd
%-------------------------------------
%---------Teaching/Leadership Experience-------
\section{Teaching/Leadership Experience}
 \resumeSubHeadingListStart
  \resumeSubItem{}{Conducted an IEEE Workshop on Basics of Web Development and Trends in Web Technology for college students (Jan 2018).}
  \resumeSubItem{}{Part of the core IT Department Coding Club (2017-2018).}
  \resumeSubItem{}{Taught Maths, Science and Music for underprivileged school kids as part of the Sri Sathya Sai Seva Organization.}
 \resumeSubHeadingListEnd
\end{document}

